\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{hyperref}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
\usepackage{tabu}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}

\hspace{0.5cm}\\[-0.2cm]

\begin{tabu}  { X[l] X[l] }

    \textbf{Balakrishna Avulapati} & \hspace{5em} Email-id \hspace{1em} : \textbf{\href{mailto:balakrishnaa@outlook.com}{balakrishnaa@outlook.com}} \\
    M.Tech Computational Mathematics & \hspace{5em} LinkedIn\hspace{1em} : \href{https://in.linkedin.com/in/balakrishnaavulapati}{balakrishnaavulapati} \\
    National Institute of Technology Karnataka & \hspace{5em} GitHub \hspace{1.4em} : \href{https://github.com/bavulapati}{bavulapati}  \\
    \textbf{(NITK)}, Surathkal. & \hspace{5em} Mobile No. : \href{tel:+918050890586}{+91 8050890586}\\
\end{tabu}

\medskip

\resheading{\textbf{OBJECTIVE} }\\[\lsep]
\begin{itemize}
    \item \noindent Pursuing career in solving real time problems using my technical skills and education.
\end{itemize}

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
    \hline
    \textbf{Examination} & \textbf{Specialization} & \textbf{University} & \textbf{Institute} & \textbf{Year} & \textbf{GPA/\%} \\
    \hline
    M.Tech & \textit{Computational Mathematics} & NIT Karnataka & NIT Karnataka & 2016 & 7.89 \\
    B.Tech & \textit{Computer Science and Engineering} & GPREC Kurnool & SKU Anantapur & 2013 & 7.28\\
    IPE (XII) & \textit{Mathematics Physics Chemistry} & BIE AP & Narayana Jr. College AP & 2009 & 94.6\\
    SSC (X) & \textit{Mathematics Social Science} & BSE AP & Bala Sai High School AP & 2007 & 87.3\\
    \hline
\end{tabular}

\medskip

\resheading{\textbf{CAREER SUMMARY} }\\[\lsep]
\begin{itemize} \itemsep \isep
    \item \noindent Working as a Programmer Analyst for IDrive Software (India) Pvt Ltd, Bangalore since July 2016.
    \item \noindent College Student Intern at EMC ICoE, Bangalore (May 2015 – May 2016)
    \item \noindent Intern at Quadrivium Software Pvt. Ltd. Hyderabad (October 2012 – May 2013)
\end{itemize}

\resheading{\textbf{FIELDS OF INTEREST} }\\[\lsep]
\begin{itemize}
    \item \noindent Mobile Application Development, Machine Learning and Theoretical Computer Science.
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
    \item \noindent \textbf{Languages} (C, C\#, Java),\textbf{Database} (MySQL), \textbf{Web Services} (REST, SOAP), \textbf{Tools} (Intellij, Visual Studio),
    \textbf{DevKits} (Android SDK). 
\end{itemize}

\resheading{\textbf{WORK EXPERIENCE} }\\[\lsep]
\begin{itemize}

    \item \textbf{Project: Encoding and Decoding optimization for RemotePC product} \\
    \emph{(Company: IDrive Software (India) Pvt Ltd.\textbf{July’2017 - Present} , Bangalore)} \\[-0.6cm] 
	\begin{itemize}\itemsep \isep
	
	    \item Description : RemotePC captures the screen and transfers the screen to remote computer. It also encodes and decodes the screen.
	    \item Studied and analyzed the encoding algorithms like Tight encoding, H265, H264. And made the proof of concept.
	    \item Studied and analyzed hardware acceleration feasibility and worked on it.

	\end{itemize}
	
    \item \textbf{Project: Remote Data feature for RemotePC product} \\
    \emph{(Company: IDrive Software (India) Pvt Ltd.\textbf{July’2016 - June’2017} , Bangalore)} \\[-0.6cm] 
	\begin{itemize}\itemsep \isep
	
	    \item Description : Remote Data feature enables user to explore, see and download the  files on host computer with and android mobile.
	    \item Developed the UI consuming the REST API. Used Fragments, services and  broadcast receivers.
	    \item Coordinated with the windows and Mac teams in developing the remote data feature.
        \item Used Android NDK for reusing the FFmpeg native library for decoding the H.264 frames received from host computer.

	\end{itemize}
\end{itemize}

\resheading{\textbf{INTERNSHIPS} }\\[\lsep]
\begin{itemize}
    \item \textbf{Project : API Automation Framework for RSA Archer eGRC product.} (M. Tech. Internship) \\
    \emph{(Company : EMC ICoE, Bangalore.May'15 – May'16)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	
	    \item Description : To automate the testing process of the REST API of Archer and publish the results at scheduled time.
	    \item Studied about REST API, implemented the framework in Java and coordinated with the testers to model the input(Excel sheet) and outputs(JUnit xml). \item Provided a GUI for them to write new test cases which stores them in an Excel sheet.
	    \item Used the JUnit output format to store the results and used Jenkins%(which maintains the results in DB and shows the results as graphs and pie charts)%
	    to schedule and publish the results
	
	\end{itemize}
	
	\item \textbf{Project : IBodha.} (B. Tech. Internship) \\
    \emph{(Company : Quadrivium Software Pvt. Ltd, Hyderabad.Oct'12 – May'13)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	
	    \item Description : IBodha brings together some of the best teachers, subject matter experts, professors, and researchers in the business, along with a host of other professionals
	    \item Understood the software development life cycle and the enterprise development.
	    \item Used JSF, Java, MySQL, SVN.
	    
    \end{itemize}

\end{itemize}

%\bigskip
%\bigskip

\resheading{\textbf{ACCOMPLISHMENTS} }\\[\lsep]
\begin{itemize} \itemsep \isep
    \item Secured AIR 1195 in GATE (CSE) 2014.
    \item Qualified the JEE and was in Extended Merit List in 2009.
    \item Rewarded by Dena Bank for securing 1st position in the school in 7th standard.
    \item Completed 5K run at Zinnov run 2015 , Shree Kanteerava Stadium, Bangalore.
\end{itemize}

\resheading{\textbf{CO-CURRICULAR ACTIVITIES} }\\[\lsep]
\begin{itemize} \itemsep \isep
    \item Volunteer teacher for the school adopted by RSA, Bangalore.
    \item Coordinated the internships for CMA in the 2nd semester.
    \item Hosted a stall in the Jignasa2011, a cultural and tech fest of GPREC, Kurnool.
    \item Presented a seminar on Haptics, science of applying touch.
\end{itemize}

\resheading{\textbf{STRENGTHS} }\\[\lsep]
\begin{itemize}
    \item \noindent Positive Attitude, Social Interaction, Hardworking.
\end{itemize}

\resheading{\textbf{INTERESTS AND HOBBIES} }\\[\lsep]
\begin{itemize}
    \item \noindent Reading Books about adventures.
    \item \noindent Swimming and Jogging.

\end{itemize}

\end{document}

